Verifying Demonstrations

### 2017-08-23 SystemModel.tex
Changes to use \mode to hide frames, fixes #10
Edits system model, intro
Moves def of protest to system model

\section{System model}
\label{SystemModel}

@@

We assume that every participant has a device similar to a smartphone.
It must be a portable device which can perform cryptographic operations and 
communicate with other devices during the protest, e.g.\ through an ad-hoc 
network.
I.e.\ no connection to the Internet is necessary during the protest.
During the protest these devices are computationally limited by their 
batteries.
Before and after the protest, we assume that the devices have Internet 
connections and are not computationally limited by any battery.

\begin{frame}<presentation>
  \begin{assumption}[During protest]
    \begin{itemize}
      \item Everyone has a smartphone.
      \item Can use ad-hoc networks during the event.
      \item Computations bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause

  \begin{assumption}[Before and after protest]
    \begin{itemize}
      \item Internet connection available.
      \item Computations not bounded by battery life.
    \end{itemize}
  \end{assumption}
\end{frame}

This means that we essentially provide a lower bound for the participation 
count, since some participants might not have any smartphone.
\begin{frame}
\begin{remark}
  We provide a lower bound, since there might be participants without phones.
\end{remark}
\begin{remark}
  I.e.\ provided we can prevent Sybil.
\end{remark}
\end{frame}

\begin{frame}<presentation>
  \begin{block}{Alice the activist}
    \begin{itemize}
      \item Alice organizes the protest against Eve's regime.
      \item Alice wants to have a high participation count.
      \item She tries to increase it.
    \end{itemize}
  \end{block}

  \pause

  \begin{block}{Eve the fake-news populist}
    \begin{itemize}
      \item Eve's regime is target of the protest.
      \item She wants to have a low participation count.
      \item She tries to decrease it.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}<presentation>
  \begin{block}{Eve the totalitarian dictator}
    \begin{itemize}
      \item Eve wants to \enquote{convince} activists to support her.
      \item She wants to find all activists.
      \item She tries to identify (deanonymize) participants.
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}<presentation>
  \begin{block}{Rusuk the nation state}
    \begin{itemize}
      \item Rusuk benefits from the situation in Evestan.
      \item He wants the outcome to be the most beneficial.
      \item He will try to increase or decrease the participation count.
    \end{itemize}
  \end{block}
\end{frame}

\subsection{System model}

We will define a protest as an event that is uniquely identified by its cause, 
its time and its location.
More specifically, we will use the following definition.

@@

\begin{frame}<presentation>
\begin{definition}[Protest]
  \begin{itemize}
    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
    \item \(id\in \Z_{2^\lambda}\) is an identifier,
    \item \((t_s, t_e)\in \R^2\) is a time interval,
    \item \((x, y)\in \R^2\) are the coordinates of the location.
    \item A \emph{protest} is a set of subprotests sharing the same \(id\).
  \end{itemize}
\end{definition}
\end{frame}

The protests described in \cref{WhatIsAProtest} can be captured using this 
definition by splitting them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.

@@

\begin{frame}
  \mode<presentation>{
  \begin{definition}[Participation proof]
    \begin{itemize}
      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; 
          \sigma)\), where
      \item \(id, t_s, t_e, x, y\) are as before.
      \item \(\sigma\) is a signature vouching for participation.
    \end{itemize}
  \end{definition}

  \pause
  }
\begin{question}
  How should this one relate to the \acp{LP} and blockchain?
\end{question}
\end{frame}

>>>>

\section{System model}%
\label{SystemModel}

@@

We assume that every participant has a device similar to a smartphone.
(This means that we essentially provide a lower bound for the participation 
count, since some participants might not have any smartphone.)
It must be a portable device which can perform cryptographic operations and 
communicate with other devices during the protest, e.g.\ through an ad-hoc 
network.
I.e.\ no connection to the Internet is necessary during the protest.
During the protest these devices are computationally limited by their 
batteries.
Before and after the protest, we assume that the devices have Internet 
connections and are not computationally limited by any battery.

\mode<presentation>{%
\begin{frame}
  \begin{assumption}[During protest]
    \begin{itemize}
      \item Everyone has a smartphone.
      \item Can use ad-hoc networks during the event.
      \item Computations bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause{}

  \begin{assumption}[Before and after protest]
    \begin{itemize}
      \item Internet connection available.
      \item Computations not bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause{}

  \begin{remark}
    We provide a lower bound, since there might be participants without phones.
  \end{remark}
\end{frame}
}

We further assume that every participant has a digital certificate signed by 
some logically centralized certificate authority.
E.g.\ that we can use the cryptographic keys stored in the chip of the national 
identity card or passport.
We need this to prevent Sybil attacks~\cite{SybilAttack}.
\begin{frame}
\begin{remark}
  I.e.\ provided we can prevent Sybil.
\end{remark}
\end{frame}

\subsection{What is \protect\emph{a} protest?}%
\label{WhatIsAProtest}

Protests can vary considerably.
To be able to estimate the participation count for one, we first need to define
what should be counted.

Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
  people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
in parallel in many locations.
We also have the Venezuelan demonstrations where
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show 
  their support for the president's controversial plan to rewrite the 
  constitution%
}.
Judging from these examples, the minimal common part is the cause.

\mode<presentation>{%
\begin{frame}
  \begin{example}[Seoul 2016]
    \begin{itemize}
      \item Rallies every weekend.
      \item Starting midday, lasting to late night.
      \item Some stayed for several hours, some for only minutes.
    \end{itemize}
  \end{example}

  \pause{}

  \begin{example}[US 2017]
    \begin{itemize}
      \item Women's Marches in several locations.
      \item Marched some distance.
      \item One-time occurrence.
    \end{itemize}
  \end{example}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{example}[Venezuela 2017]
    \begin{itemize}
      \item Daily anti-government rallies.
      \item Multiple locations.
      \item Pro-government rallies too.
    \end{itemize}
  \end{example}
\end{frame}
}

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We will define a protest as an event that is uniquely identified by its cause, 
its time and its location.
More specifically, we will use the following definition.

@@

\mode<presentation>{%
\begin{frame}
\begin{definition}[Protest]
  \begin{itemize}
    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
    \item \(id\in \Z_{2^\lambda}\) is an identifier,
    \item \((t_s, t_e)\in \R^2\) is a time interval,
    \item \((x, y)\in \R^2\) are the coordinates of the location.
    \item A \emph{protest} is a set of subprotests sharing the same \(id\).
  \end{itemize}
\end{definition}
\end{frame}
}

The protests described above can be captured using this definition by splitting 
them up into subprotests.
Each subprotest will then be captured by our definition and to find the total 
we can just sum up the results.

@@

\begin{frame}
  \mode<presentation>{%
  \begin{definition}[Participation proof]
    \begin{itemize}
      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; 
          \sigma)\), where
      \item \(id, t_s, t_e, x, y\) are as before.
      \item \(\sigma\) is a signature vouching for participation.
    \end{itemize}
  \end{definition}

  \pause{}
  }
\begin{question}
  How should this one relate to the \acp{LP} and blockchain?
\end{question}
\end{frame}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Alice the activist}
    \begin{itemize}
      \item Alice organizes the protest against Eve's regime.
      \item Alice wants to have a high participation count.
      \item She tries to increase it.
    \end{itemize}
  \end{block}

  \pause{}

  \begin{block}{Eve the fake-news populist}
    \begin{itemize}
      \item Eve's regime is target of the protest.
      \item She wants to have a low participation count.
      \item She tries to decrease it.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Eve the totalitarian dictator}
    \begin{itemize}
      \item Eve wants to \enquote{convince} activists to support her.
      \item She wants to find all activists.
      \item She tries to identify (deanonymize) participants.
    \end{itemize}
  \end{block}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Rusuk the nation state}
    \begin{itemize}
      \item Rusuk benefits from the situation in Evestan.
      \item He wants the outcome to be the most beneficial.
      \item He will try to increase or decrease the participation count.
    \end{itemize}
  \end{block}
\end{frame}
}

### 2017-08-23 intro.tex
Cleans up contents
Adds WIP on system model
Removes what's a protest from slides
Adapts intro: moves why it's a problem
Breaks privacy out of intro (again)
Changes to use \mode to hide frames, fixes #10
Edits system model, intro
Moves def of protest to system model

\section{Introduction}
\label{Introduction}

@@

\begin{frame}<presentation>
  \begin{example}
    \begin{itemize}
      \item Computer vision does object recognition.
      \item Requires photos/video that cover the entire location, all the time.
      \item This will count people twice.
    \end{itemize}
  \end{example}

  \pause

  \begin{example}
    \begin{itemize}
      \item Scan active mobile phones in the area.
      \item This requires some extra equipment.
      \item This catches bystanders who are not protesting.
    \end{itemize}
  \end{example}
\end{frame}

@@

\begin{frame}<presentation>
  \begin{example}
    \begin{itemize}
      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
        approximate count by imagery.
        \begin{description}
          \item[Police] X
          \item[Organizers] Y
        \end{description}

        \pause

      \item US 2017~\cite{2017WomensMarchesInUS}:
        sum up people's approximations.
      \item This makes it even difficult to estimate the error.
    \end{itemize}
  \end{example}
\end{frame}

@@

\subsection{What is \protect\emph{a} protest?}

Protests can vary considerably.
To be able to estimate the participation count for one, we first need to define
what should be counted.

Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
  people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every 
weekend for the duration of a few weeks.
The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
in parallel in many locations.
We also have the Venezuelan demonstrations where
\blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show 
  their support for the president's controversial plan to rewrite the 
  constitution%
}.
Judging from these examples, the minimal common part is the cause.

\begin{frame}<presentation>
  \begin{example}[Seoul 2016]
    \begin{itemize}
      \item Rallies every weekend.
      \item Starting midday, lasting to late night.
      \item Some stayed for several hours, some for only minutes.
    \end{itemize}
  \end{example}

  \pause

  \begin{example}[US 2017]
    \begin{itemize}
      \item Women's Marches in several locations.
      \item Marched some distance.
      \item One-time occurrence.
    \end{itemize}
  \end{example}
\end{frame}

\begin{frame}<presentation>
  \begin{example}[Venezuela 2017]
    \begin{itemize}
      \item Daily anti-government rallies.
      \item Multiple locations.
      \item Pro-government rallies too.
    \end{itemize}
  \end{example}
\end{frame}

The organizer Alice want to count everyone who participated at any time and in 
any of the locations~\cite{2016DemonstrationsInSeoul}.
(Whereas police are only interested in the maximum crowd at any point in time, 
to deploy enough personnel for crowd-control.)
We thus settle for the following definition.

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item Organizers want to count anyone who participated \dots
      \item \dots at any time
      \item \dots in any location
    \end{itemize}
  \end{remark}
\end{frame}

\begin{frame}
\begin{definition}[A protest]
  A protest is an event identified by its cause.
\end{definition}
\end{frame}

% Verifiability and privacy
\mode<all>
\input{properties.tex}

\subsection{Contributions}

In this paper, we combine the verifiability and privacy properties of 
electronic voting with location-proof systems to provide a verifiable 
participation count.

@@

\blockcquote{HowToEstimateCrowdSize}{%
  Crowd size is also needed for media news reports and to historically record 
  the event%
}

>>>>

\section{Introduction}%
\label{Introduction}

@@

@@

\mode<presentation>{%
\begin{frame}
  \begin{example}
    \begin{itemize}
      \item Computer vision does object recognition.
      \item Requires photos/video that cover the entire location, all the time.
      \item This will count people twice.
    \end{itemize}
  \end{example}

  \pause{}

  \begin{example}
    \begin{itemize}
      \item Scan active mobile phones in the area.
      \item This requires some extra equipment.
      \item This catches bystanders who are not protesting.
    \end{itemize}
  \end{example}
\end{frame}
}

\mode<presentation>{%
\begin{frame}
  \begin{example}
    \begin{itemize}
      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
        approximate count by imagery.
        \begin{description}
          \item[Organizers] 1\,000\,000
          \item[Police] 260\,000
        \end{description}

        \pause{}

      \item US 2017~\cite{2017WomensMarchesInUS}:
        sum up people's approximations.
      \item This makes it even difficult to estimate the error.
    \end{itemize}
  \end{example}
\end{frame}
}

@@

\subsection<article>{Contributions}

In this paper, we combine the verifiability and privacy properties of 
electronic voting with location-proof systems to provide a verifiable 
participation count.
We can only provide a verifiable participation count for non-government 
protests:
In any pro-government protest we cannot prevent the government from doing a 
Sybil attack, since the government controls the identity system.

@@

%\blockcquote{HowToEstimateCrowdSize}{%
%  Crowd size is also needed for media news reports and to historically record 
%  the event%
%}
